Updates on the Exoplanet Orbit Database

### 2014-02-18 draft/ms.tex
Orbital parameter section update

LAMBDA: the literature has conflicted definitions of LAMBDA, and we
sorted it out and made sure it is consistent in EOD.

LAMBDA: We report the projected spin-orbit misalignment of transiting systems. We follow the definition of Fabrycky and Winn 2009.

>>>>

LAMBDA: We report the projected spin-orbit misalignment of transiting systems. We follow the definition of Fabrycky and Winn 2009. The spin-orbit angle is defined to be the angle between the stellar spin axis and the orbital axis. However, since the spin-orbit angle is not directly measurable, and therefore lambda, the projected spin-orbit angle was introduced. In the observer-oriented frame, Z axis points toward the observer, X axis points along the intersection of the sky plane and the planet's orbital plane, and Y axis completes a right handed-triad. Lambda is measured clockwise on the sky from the Y axis to the projected stellar rotational axis. While maintaining LAMBDA in our database, we figured out that literatures have conflicted definitions of LAMBDA with $\beta$, which is equal to $\lambda$ = -$\beta$. We sorted these cases out and made sure that LABDA is following the definition of Fabrycky and Winn 2009.
